Self Regulation Ontology Retest Analyses

### 2018-07-25 code/SRO_Retest_Analyses.Rmd
updating stats

```{r}
summary(lm(value~key*similarity,tmp))
```

```{r}
summary(MCMCglmm(value ~ key*similarity, data=tmp, nitt = 50000)) 
```

@@

```{r}
summary(lm(sample_size ~ task,rel_comp))
```

@@

```{r}
summary(mod2)
```

@@

tmp %>%
  ggplot(aes(sample_size, resid))+
  geom_point()+
  geom_smooth(method = "lm")

summary(lm(resid ~ sample_size, tmp))
```

>>>>

```{r}
summary(lm(value~key*scale(similarity),tmp))
```

```{r}
summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000)) 
```

@@

```{r}
# summary(lm(sample_size ~ task,rel_comp))
summary(m1 <- MCMCglmm(sample_size ~ task, data=rel_comp))
```

@@

```{r}
#summary(mod2)
summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp))
```

@@

tmp %>%
  ggplot(aes(sample_size, resid))+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r}
summary(lm(resid ~ sample_size, tmp))
```
